\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{xurl}

\title{Unit Test Status Report}
\author{Scrubbing Project}

\begin{document}
\maketitle

\section*{Overall Status}
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Test Class} & \textbf{Executed} & \textbf{Passed} & \textbf{Failed} \\
\hline
\texttt{DigitScrubberTest} & 8 & 4 & 4 \\
\hline
\texttt{EmailScrubberTest} & 11 & 10 & 1 \\
\hline
\texttt{ScrubTest} & 5 & 3 & 2 \\
\hline
\textbf{Total} & \textbf{24} & \textbf{17} & \textbf{7} \\
\hline
\end{tabular}
\end{center}

\section*{What Passed}
\begin{itemize}
  \item Core scrubbing behavior works in normal paths: email-only, digits-only, and full-scrub happy paths.
  \item Most edge cases pass: 17 of 24 tests succeeded.
\end{itemize}

\section*{Failed Tests and Justification}
\renewcommand{\arraystretch}{1.2}
\begin{longtable}{|>{\raggedright\arraybackslash}p{0.32\textwidth}|>{\raggedright\arraybackslash}p{0.22\textwidth}|>{\raggedright\arraybackslash}p{0.38\textwidth}|}
\hline
\textbf{Failed Test} & \textbf{Observed Failure} & \textbf{Justification} \\
\hline
\endfirsthead
\hline
\textbf{Failed Test} & \textbf{Observed Failure} & \textbf{Justification} \\
\hline
\endhead

\url{testScrubDigits_PriceNotScrubbed} & \texttt{100\$} became \texttt{XXX\$}. & Digit logic replaces all digits globally; there is no price-preservation rule. \\
\hline

\url{testScrubDigits_DecimalPriceNotScrubbed} & \texttt{100.50\$} became \texttt{XXX.XX\$}. & Decimal currency format is not exempted from digit masking. \\
\hline

\url{testScrubDigits_CommaSeparatedPriceNotScrubbed} & \texttt{1,000\$} became \texttt{X,XXX\$}. & Comma-separated currency also gets fully digit-masked; missing protected-token handling. \\
\hline

\url{testScrubDigits_PlaceholderLikeUserTextShouldRemainUntouched} & Price digits changed to \texttt{XXX\$}. & Scrubber has no context-sensitive distinction between sensitive digits and allowed price literals. \\
\hline

\url{testScrubEmail_EmptyString} & Exception type mismatch. & Blank input currently throws \texttt{NullPointerException}; test expects \texttt{IllegalArgumentException}. \\
\hline

\url{testScrubPrompt_InvalidScrubbingMode} & Expected exception not thrown. & \texttt{MainScrubber} catches mode/input exceptions and returns \texttt{null}, so the expected \texttt{IllegalArgumentException} is skipped. \\
\hline

\end{longtable}

\end{document}
